---
title: "OSM Data App"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OSM Data App}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab05)
```

# What is this package?

The OSM Data App is a GUI application meant to find a city and retrieve data from Open Street Maps API. These data are coordinates plotted on a map plots of establishments instances of user choice (ATMs, pharmacies, hospitals, supermarkets and gas stations). 

## osmObjects Class

This class takes 2 **Character** type inputs named  **city** (an actual city name) and an type of establishment (**object**) contained in this list: **ATMs**, **pharmacies**, **hospitals**, **supermarkets** and **gas stations**. The class uses outside functions **getBoundingBox** and *getElements** to request for a boundary box of the city passed and the coordinates of the object demanded respectively. 

### Methods

#### plot

Uses **ggmap** and **ggplot2** to plot the city in a map with marked coordinates of the object passed over this map.
Example:

```{r include = TRUE}
Barcelona <- osmObjects(city="Barcelona", object="hospital")
Barcelona$plot()
```
 
#### print

Prints coordinates of requested objects
Example:

```{r include = TRUE}
Barcelona <- osmObjects(city="Barcelona", object="hospital")
Barcelona$print()
```

### Functions used inside osmObjects Class

#### getBoundingBox 
Gets request for boundary box of the element **city** where the object coordinates will be located. The argument passed (**city**) should be a **character**. The output obtained will be a 2x2 Matrix.
Example:

```{r include = TRUE}
getBoundingBox("Barcelona")
```

#### getElements

Gets request for element from overpass API. Its arguments are **bbox**, **key**, **value**. The **bbox** is the bounding box obtained out of the  **getBoundingBox** function, a matrix. The **key-value** pair is a couple of character variables from this mapping:

```{r include = TRUE}
table = cbind(c("atm", "bank", "pharmacy", "hospital", "supermarket", "fuel"), c("amenity", "amenity", "amenity", "amenity", "shop", "amenity" ))

knitr::kable(
  table, caption = 'Key-Value pairs'
)
```

Finally, it retrieves the coordinates for the object demanded inside the **bbox** boundaries in a **data.frame**. 
Example:

```{r include = TRUE}
Barcelona_bbox <- getBoundingBox("Barcelona")

getElements(Barcelona_bbox, "amenity", "hospital")
```

